### 2014-08-11 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG County: update report, input files, and add department report

The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure. Based on the goals of the analysis and the information collected, several engineering approximations were made. For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known. The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations. The HRR of the fire was estimated using documentation of the potential fuel load within the structure.

@@

\section{Mesh}
\label{mesh}

@@

\bibliography{../Bibliography/FDS_refs,../Bibliography/FDS_general,../Bibliography/FDS_mathcomp}

>>>>

The analysis of the simulation results is focused on the impact of ventilation, specifically opening and closing the front door, on the conditions on the first floor of the structure.

@@

\section{Numerical Mesh}
\label{mesh}

@@

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
